---
title: "Untitled"
output:
  github_document: default

date: "2023-09-20"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r}
library(moderndive)
library(ggplot2)
library(tidyverse)
#import the data 
data("early_january_weather")
early_january_weather
str(early_january_weather)
nrow(early_january_weather)
ncol(early_january_weather)
mean(early_january_weather$temp)
#use ggplot to create the scatter point plot for the data
ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) + geom_point()
ggsave("scatter_plot.pdf", height = 4, width = 6)
```
Discription: The dataset contain 358 rows, 15 columns, and with the mean temperature of 39.58. Within these 15 variables there is "temp", which represents the temperature (in degrees Fahrenheit) observed at that hour. There is "humid", which represents the humidity level observed at that hour. there is "time_hour", which represents the specific hour of observation. There is "Wind_speed", which represents the wind speed observed at that hour.
```{r}
library(tidyverse)
#set a normal distribution and pick number randomly from the normal distribution
a = rnorm(10)
#create a dataframe 
df <- data.frame(
  a,
  logical_vector = a > 0,
  char_vector    = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
  factor_vector  = factor(rep(1:3, length.out = 10))
)
#print the dataframe
print(df)
#take the mean of a variable in the dataframe with "pull" function
mean_numeric <- mean(pull(df, a))
mean_numeric
mean_logical <- mean(pull(df, logical_vector))
mean_logical
#Convert to Numeric
x=as.numeric(mean_numeric)
y=as.numeric(mean_logical)
#print the numeric 
x
y
```

